---
title: "WUP_04"
author: "Sarah Medina"
date: "fall 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
writeup4data <- read.csv(file="GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

In order to analyze the results we will use a box plot to compare the median of WORDSUM scores given the level of a persons schooling degree. We will also use the My tricks file to convert the categories into factor variables.

```{r eval=FALSE}
writeup4data <- writeup4data %>%
mutate(across(where(is.character), as.factor))
```
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
boxplot(WORDSUM~DEGREE,data=writeup4data)
```

The box plot demonstrates a statistical difference between the Wordsum scores of students in Lt High School and those in Graduate school.If we were to align the results from the Lt High School;while, maintaining it's same altitude with the results form those in Graduate school into the same column the two results would not intersect with each other. Thus, indicating a statistical difference between Lt High School and Graduate School Wordsum scores. 

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results


```{r}
favstats(WORDSUM~DEGREE,data=writeup4data)
```

 The numerical results show that the mean for those in Graduate School is 10 unlike the Lt High School which has a mean of 8.
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
model1 <- aov(WORDSUM~DEGREE,data=writeup4data)
summary.aov(model1)
```

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
